\begin{topic}{Professional Experience}
\proj{St Paul's Girls School}{https://spgs.org/}{11 September 2020}{7 February 2021}{Brighton}
\detail{
 Taught two courses: mechatronics class, to a group of students, which built an automated candy dispenser and game programming in Unity, one on one with a sixth form student.
 \BulletItem
  Built a scheme of work for a Computer Science GCSE.
}

\proj{Microsoft Research LTD}{}{1 April 2012}{5 April 2012}{Cambridge}
\detail{
 Human Experience \& Design and Machine Learning teams
 \BulletItem
 Programmed the .Net Gadgeteer in C\# and shadowed the Human Experience \& Design and Machine Learning teams.
}

\proj{Thrive Wearables}{https://www.thrivewearables.com/}{2 March 2020}{26 July 2020}{Brighton}
\detail {
Embedded Intelligence Engineer
\BulletItem
Worked on various embedded wearable products using Arduino, Nordic nrf52, C, C++, Assembly and electronics.
\BulletItem
Used the Jetson Nano to build a Computer Vision Solution for emotional state recognition with python and Cuda/C++ including Machine Learning and developed multiple Android companion apps from scratch.
\BulletItem
Set up automation for business pipeline, provisioned and set up AWS services for internal and external use and wrote reports and user guides for the various projects.
}
\proj{Brighton College}{https://www.brightoncollege.org.uk/}{22 August 2018}{15 November 2018}{Brighton}
\detail{
PGAT Computer Science
\BulletItem
Taught Computer Science to one GCSE and one year 9 class, tutored A-level students and aided in other lessons.
\BulletItem
Year 7 co-tutor and boarding duty (Ages 13-18): handled registration, pastoral care, prep and lights off.
\BulletItem
Other duties such as supervised prep, boarders computer science club, contributions to the VLE and creation of resources.
}
\proj{Credit Suisse}{https://www.credit-suisse.com/uk/en.html}{10 April 2017}{22 September 2017}{London}
\detail{
Six Month Industrial Placement: Application Developer for Credit eTrading. Was offered full time job for August 2018.
\BulletItem
Backtesting Reports, generating reports for the Quants: Java \& Bash.
\BulletItem
Algo PKI, adding TLS to the Algo trading framework site: Java.
\BulletItem
Reg-Reporter, a reporting system for the MIFID-II regulation made compatible for other teams to also use: Java.
}


\end{topic}